---
title: "Project 3: project3package Tutorial"
author: "Wan Yee Hing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{project3package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

In Statistics, we talk a lot about statistical inference and prediction. So, we
introduce **project3package** here to provide some functions to handle
statistical inference and statistical prediction. Specifically,
**project3package** provides four functions:
* my_t.test function
* my_lm function
* my_knn_cv function
* my_rf_cv function

To install **project3package**, use the following code:
```{r install, eval = FALSE}
devtools::install_github("wanyeehing/project3package")
```

To begin, we load the **project3package**.
```{r setup}
library(project3package)
```

## Tutorial for my_t.test

Now, I will demonstrate on how to use the my_t.test function provided in
**project3package**.

In this section, we are going to use the `lifeExp` data from `my_gapminder`,
so we need to run the following line of code.
```{r}
life_exp <- my_gapminder$lifeExp
```

First of all, let us see how to test the hypothesis:
$$
H_0: \mu = 60,\\
H_a: \mu \neq 60.
$$

To do it, we call the `my_t.test` function using the following way:
(Note that we use "two.sided" as the alternative as our alternative hypothesis
is $\mu \neq 60$)
```{r}
my_t.test(life_exp, alternative = "two.sided", mu = 60)
```

By looking at the result given by the function, we can see that the p-value we
get in this hypothesis testing is
`r round(my_t.test(life_exp, alternative = "two.sided", mu = 60)$p_val, 3)`. The
p-value we get is greater than our cut-off $\alpha = 0.05$. So, we conclude
that we do not have enough evidence to reject the null hypothesis that
$\mu = 60$.

Next, let us take a look on how to test another hypothesis:
$$
H_0: \mu = 60,\\
H_a: \mu < 60.
$$

In this case, the alternative hypothesis have the $<$ sign, so we will use
"less" as the alternative when using the `my_t.test` function.
```{r}
my_t.test(life_exp, alternative = "less", mu = 60)
```

From this test, we also notice that our p-value,
`r round(my_t.test(life_exp, alternative = "less", mu = 60)$p_val, 3)` is
greater than $\alpha = 0.05$. Therefore, we also fail to reject the null
hypothesis that $\mu = 60$.

For the last case where the alternative hypothesis have the $>$ sign,
$$
H_0: \mu = 60,\\
H_a: \mu > 60.
$$
we will use the following code:

```{r}
my_t.test(life_exp, alternative = "greater", mu = 60)
```

In the last case, we see that the p-value is
`r round(my_t.test(life_exp, alternative = "greater", mu = 60)$p_val, 3)`.
This p-value is less than $\alpha = 0.05$, so we have enough evidence to
reject the null hypothesis, $\mu = 60$.

## Tutorial for my_lm
