---
title: "Project 3: project3package Tutorial"
author: "Wan Yee Hing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{project3package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

In Statistics, we talk a lot about statistical inference and prediction. So, we
introduce **project3package** here to provide some functions to handle
statistical inference and statistical prediction. Specifically,
**project3package** provides four functions:
* my_t.test function
* my_lm function
* my_knn_cv function
* my_rf_cv function

To install **project3package**, use the following code:
```{r install, eval = FALSE}
devtools::install_github("wanyeehing/project3package")
```

To begin, we load the **project3package**.
```{r setup}
library(project3package)
```

# Tutorial for my_t.test

Now, I will demonstrate on how to use the my_t.test function provided in
**project3package**.
