---
title: "Project 3: project3package Tutorial"
author: "Wan Yee Hing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{project3package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

\addtolength{\headheight}{-.025\textheight} 
\thispagestyle{fancyplain} 
\rhead{\includegraphics[height=.1\textheight]{logo.png}}
\renewcommand{\headrulewidth}{0pt}

# Introduction

In Statistics, we talk a lot about statistical inference and prediction. So, we
introduce \texttt{project3package} here to provide some functions to handle
statistical inference and statistical prediction. Specifically,
\texttt{project3package} provides four functions:
\begin{itemize}
\item my_t.test function
\item my_lm function
\item my_knn_cv function
\item my_rf_cv function
\end{itemize}

To install \texttt{project3package}, use the following code:
```{r install, eval = FALSE}
devtools::install_github("wanyeehing/project3package")
```

To begin, we load the project3package.
```{r setup}
library(project3package)
```

# Tutorial for my_t.test


